author_name

### 2021-03-03 inst/examples/author_name.Rmd
update

* `r length(unique(df$author_name))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
 * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
 * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
 * `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
 * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

>>>>

* `r length(unique(df$author_name))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
 * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
 * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))-2` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
 * `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
 * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.
